### 2020-11-02 thesis/chap_1.tex
add AAFC, comment 9
comment 7

% [what about those models in CC context?]
Connectivity researchers have studied how past changes in land use can explain current connectivity patterns \citep{dupras_urban_2015, henareh_khalyani_spatial_2013, vergara_deforestation_2013, patru-stupariu_using_2013} and multiple connectivity measures have been developed, one specifically in this context \citep{saura_new_2007}. But beyond these historical analyses, land use models are becoming more common \citep{correa_ayram_habitat_2015}. For example, \cite{rubio_sustaining_2012} identified a network of forest patches resilient to land use change under multiple scenarios in Spain. Similarly, \cite{piquer-rodriguez_future_2012} integrated land use change and connectivity models to identify under-protected areas by projecting land use change trends. \cite{huang_simulating_2018} also used land use change models to assess potential impacts on functional connectivity in China. \cite{albert_applying_2017} used a land use change model to forecast changes in species networks. From these examples, we can see that combining land use change modelling and connectivity modelling does not yet have a fully established methodology. In its emerging form, it simply consists of running a land use change model on a given landscape, and comparing changes in the connectivity measure of choice between time steps \citep{perkl_urban_2018}.

@@

For most modelling frameworks, the raw source of land use change data is remote sensing data. Because producing land use change data from remotely sensed imagery was beyond the scope of this thesis, we looked for a curated dataset. Agriculture and Agri-Food Canada (AAFC) produces a dataset of land use in Canada at a 10 years interval and at the resolution of 30 meters (the resolution is the dimension of a pixel in a spatial grid, or raster data, and is an important property of land use datasets). This dataset provides land use data for the years of 1990, 2000, 2010. We found this data product, referred to hereafter as the AAFC data  to be the right fit for our approach: the data production method of the AAFC  data is consistent, meaning that similar methods have been used to produce all three maps at different time points. Consistency in data production methods is key as it makes the computation of change between time points more reliable.

>>>>

% [what about those models in CC context?]
Connectivity researchers have studied how past changes in land use can explain current connectivity patterns \citep{dupras_urban_2015, henareh_khalyani_spatial_2013, vergara_deforestation_2013, patru-stupariu_using_2013} and multiple connectivity measures have been developed, one specifically in the context of landscape planning \citep{saura_new_2007}. But beyond these historical analyses, land use models are becoming more common \citep{correa_ayram_habitat_2015}. For example, \cite{rubio_sustaining_2012} identified a network of forest patches resilient to land use change under multiple scenarios in Spain. Similarly, \cite{piquer-rodriguez_future_2012} integrated land use change and connectivity models to identify under-protected areas by projecting land use change trends. \cite{huang_simulating_2018} also used land use change models to assess potential impacts on functional connectivity in China. \cite{albert_applying_2017} used a land use change model to forecast changes in species networks. From these examples, we can see that combining land use change modelling and connectivity modelling does not yet have a fully established methodology. In its emerging form, it simply consists of running a land use change model on a given landscape, and comparing changes in the connectivity measure of choice between time steps \citep{perkl_urban_2018}.

@@

For most modelling frameworks, the raw source of land use change data is remote sensing data. Because producing land use change data from remotely sensed imagery was beyond the scope of this thesis, we looked for a curated dataset. Agriculture and Agri-Food Canada (AAFC) produces a dataset of land use in Canada at a 10 years interval and at the resolution of 30 meters (the resolution is the dimension of a pixel in a spatial grid, or raster data, and is an important property of land use datasets). This dataset provides land use data for the years of 1990, 2000, 2010 \citep{aafc_land_2020}. We found this data product, referred to hereafter as the AAFC data  to be the right fit for our approach: the data production method of the AAFC  data is consistent, meaning that similar methods have been used to produce all three maps at different time points. Consistency in data production methods is key as it makes the computation of change between time points more reliable.
